Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-18 WRITEUP/ms.tex
edits on MR relation

\begin{figure*}
\centering
\includegraphics[trim=30 30 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right). Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). 
Data points in the $\alpha_{\rm vir}$-mass figure are taken from \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein.
\DL{for some reason, I can't change the yaxis-limit first the top plots..}
\label{fig:larsons_single}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to lines of constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. \AP{please implement the following} The reference lines with different $A_V$ are computed from \Eq{constantcolumndensity}.
\DL{Ignore the blue dotted line for now.}
\label{fig:MR}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right). Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). 
Data points in the $\alpha_{\rm vir}$-mass figure are taken from \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein (see Fig 4 of \citealt{Kauffmann17b}).
\label{fig:larsons_single}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to lines of constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. \AP{please implement the following} The reference lines with different $A_V$ are computed from \Eq{constantcolumndensity}.
\DL{Ignore the blue dotted line for now.}
\label{fig:MR}}
\end{figure*}
